The Driving Forces Behind API Evolution

### 2015-05-20 thesis/paper.tex
RQ2 results+table

\subsection{Reverse Engineering API Change Decisions}

After cross-examining our initial analysis with the interviewee's responses, we found that 85\% of our main type predictions matched the actual motive of the change and that 85\% of our secondary type predictions were correct. The kappa value \cite{cohen1968weighted} for the predictions was 0.812, which shows that there is a high level of agreement between the predictions and the change decisions.

@@

>>>>

\subsection{Reverse Engineering API Change Decisions}
After cross-examining our initial analysis with the interviewee's responses, we found that 85\% of our main type predictions matched the actual motive of the change and that 85\% of our secondary type predictions were correct. The kappa value \cite{cohen1968weighted} for the predictions was 0.812, which shows that there is a high level of agreement between the predictions and the change decisions. In Table \ref{table:reverse_engineering}, a detailed view of each prediction juxtaposed against the actual change decision can be found for both the main and secondary types.

@@

\begin{table}
       \centering
       \begin{tabular}[ht]{  c | c !{\vrule width 1.5pt} c|c} 
              \toprule

              \multicolumn{2}{c !{\vrule width 1.5pt} }{\textbf{Main}}       & \multicolumn{2}{c}{\textbf{Sub}}        \\ \hline

              \textbf{Prediction}         & \textbf{Actual}            & \textbf{Prediction}       & \textbf{Actual}         \\ \Xhline{2\arrayrulewidth}
              Enhancive                   & Enhancive                 & N/A                       & N/A                \\ \hline
              Enhancive                   & Enhancive                 & N/A                       & N/A                \\ \hline
              Enhancive                   & Enhancive                 & N/A                       & N/A                \\ \hline
              Enhancive                   & Enhancive                 & N/A                       & N/A                \\ \hline
              Enhancive                   & Enhancive                 & Groomative                & Groomative         \\ \hline
              Enhancive                   & Enhancive                 & Groomative                & Groomative         \\ \hline
              Enhancive                   & Enhancive                 & Groomative                & Groomative         \\ \hline
              Reductive                   & Reductive                 & N/A                       & N/A                \\ \hline
              Adaptive                    & Adaptive                  & N/A                       & N/A                \\ \hline
              Preventive                  & Preventive                & Groomative                & Groomative         \\ \hline 
              Updative                    & Updative                  & Reformative               & Reformative        \\ \hline
              Updative                    & Reformative               & Reformative               & Updative           \\ \hline
              Groomative                  & Preventive                & Preventive                & Groomative         \\

              \bottomrule
       \end{tabular}
       \caption{Categorisation of Changes }
       \label{table:reverse_engineering}
\end{table}
